Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-07-30 paperIEEE.tex
Reviewer 1, Collage tests
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@138 db7c848b-7755-4df2-b763-8796797afa52
Reviewer 1, typos
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@139 db7c848b-7755-4df2-b763-8796797afa52

RTT Scale uses a master-slave execution mode, were a single running Deltagen
instance can go into ``Scale mode'' at any time by launching an
\textsf{Equalizer} configuration. Consequently, the whole internal
representation needed for rendering is based on a \textsf{Collage}-based data
distribution. The rendering clients are separate, smaller applications which
will map their scenes during startup. At runtime, any change performed in the
main application is committed as a delta at the beginning of the next frame,
following a design pattern similar to the \textsf{Collage Serializable}
(\sref{sec:Serializable}). Multicast (\sref{sec:RSP}) is used to keep data
distribution times during session launch reasonable for larger cluster sizes
(tens to hundreds of nodes).

@@

During data synchronization, the master commits the object data to all mapped
slave instances simultaneously. This is a ``push'' operation, whereas the
mapping is a slave-triggered ``pull'' operation. Slave nodes queue this data and
consume it during synchronization. We test the time to commit and sync the data
using different compression engines.

>>>>

RTT Scale uses a master-slave execution mode, where a single running Deltagen
instance can go into ``Scale mode'' at any time by launching an
\textsf{Equalizer} configuration. Consequently, the whole internal
representation needed for rendering is based on a \textsf{Collage}-based data
distribution. The rendering clients are separate, smaller applications which
will map their scenes during startup. At runtime, any change performed in the
main application is committed as a delta at the beginning of the next frame,
following a design pattern similar to the \textsf{Collage Serializable}
(\sref{sec:Serializable}). Multicast (\sref{sec:RSP}) is used to keep data
distribution times during session launch reasonable for larger cluster sizes
(tens to hundreds of nodes).

@@

During data synchronization, the master commits the object data to all mapped
slave instances simultaneously. This is a ``push'' operation, whereas the
mapping is a slave-triggered ``pull'' operation. Furthermore, the buffers only
have to be serialized and compressed once, and then can be sent directly to all
mapped slave nodes. Slave nodes queue this data and consume it during
synchronization. In contrast, object mapping needs to wait for each slave node
to request the mapping, and then may need to reserialize and compress the
object data. We test the time to commit and sync the data using different
compression engines.
